DeepSched: A Deep Representation Of Scheduling Policies For Heterogeneous Distributed Systems

### 2020-04-12 paper/core/methodology.tex
added abstract
added extra evaluation figure
methodology review

In this work, we study the ability of neural networks to approximate some heuristic methods and explore its accuracy and execution time against heuristic and approximated methods.

@@

\subsection{Baseline}
Two baseline methods are considered. We choose \emph{Heterogeneous Earliest Finish Time} (HEFT) \cite{993206} to be our heuristic baseline, as it's one of the widely-used scheduling algorithms in heterogeneous systems. Also, genetic algorithms \cite{article2} is provided as an approximate baseline. \\

\subsubsection{Heterogeneous Earliest Time First (HEFT)}
HEFT \cite{993206} is an old and well-established algorithm for scheduling in heterogeneous systems. It has been used as a baseline in research due to its near-optimal results. Basically, it chooses some process to run on some machine, if the former has the earliest finish time, with considering the special nature of the heterogeneous system. However, HEFT isn't practical for real-world systems, as no-one can know in advance the finish time of a process \\

@@

The targeted \emph{fitness function} is the average waiting time $W_t$ for all tasks. The fitness function for a specific schedule \emph{S} is given by:
\begin{equation}
\mathcal Fitness(S) = \frac{\sum_{i=1}^{N} W_{ti}}{N} \label{eq:ga}
\end{equation}

\subsection{Neural Networks (Deep Learning)}
The main novel idea of this work is the use of \emph{neural networks} for the scheduling problem. Neural Networks are known to be very good at learning representations and function approximation. In this work, we propose an architecture that can be used to reach a good approximated solution for the scheduling problem. \emph{Offline Optimization} of neural networks is to be used, in order to be able to train the network on scheduling samples and then use the trained network to do inference. We avoid using \emph{online optimization}, as it's slow and we mainly care about execution time of the scheduling method.

@@

\subsubsection{Objective Function}
The cost function defined for this architecture is a sum of two criteria. Categorical cross entropy \emph{(CE)} on the predicted machine to run a specific job $M_p$ and mean square error \emph{(MSE)} on the predicted actual start time $AST_p$ and the predicted actual finish time $AFT_p$. So it can be summarized as follows:
\begin{equation}
\mathcal Loss(L) = CE(M_p, M_t) + MSE(AT_p, AT_t) \label{eq:l}
\end{equation}
where $M_p$ is the predicted machine, $M_t$ is the ground truth machine, $AT_p$ is the predicted actual time range and $AT_t$ is the ground truth actual time range. \\

\subsubsection{Drawbacks}
The main downside of the proposed solution is that we have to know the maximum number of machines and the maximum number of tasks to be able to define the network. These numbers are used to define the network and loss function dimensions.

>>>>

We study the ability of neural networks to approximate some heuristic methods and explore its accuracy and execution time against both heuristic and approximated methods.

@@

\subsection{Baseline}
Two baseline methods are considered. We choose \emph{Heterogeneous Earliest Finish Time} (HEFT) \cite{993206} to be our heuristic baseline, as it's one of the widely-used scheduling algorithms in heterogeneous systems. Also, genetic algorithms \cite{article2} is provided as a baseline for approximate methods. \\

\subsubsection{Heterogeneous Earliest Time First (HEFT)}
HEFT \cite{993206} is an old and well-established algorithm for scheduling in heterogeneous systems. It has been used as a baseline in research due to its near-optimal results. Basically, it's a greedy algorithm that chooses some process to run on some machine, if the former has the earliest finish time, with consideration of the special nature of the heterogeneous system. However, HEFT isn't practical for real-world systems, as the finish time of a process isn't usually known in advance. Also, the greedy nature of the HEFT scheduler makes it prone to failure in complex situations. \\

@@

The targeted \emph{fitness function} is the average waiting time $W_t$ for all tasks. The fitness function for a specific schedule \emph{S} is given by:
\begin{equation}
\mathcal Fitness(S) = \frac{\sum_{i=1}^{N} W_{ti}}{N} \label{eq:ga}
\end{equation}
where \emph{N} is the number of tasks in the schedule, $W_t$ is the waiting time for a specific task.

\subsection{Neural Networks (Deep Learning)}
The main novel idea of this work is the use of \emph{neural networks} for the scheduling problem. Neural Networks are known to be very good at learning representations and function approximation. In this work, we propose an architecture that can be used to reach a good approximated solution for the scheduling problem. \emph{Offline Optimization} of neural networks is to be used, in order to be able to train the network on scheduling samples and then use the trained network to do inference. We avoid using \emph{online optimization}, used in some fields such as neural style transfer \cite{gatys2015neural}. This is because it's slow and we mainly care about execution time of the scheduling method.

@@

Basically, the classifier is used during inference to produce the required schedule by determining the required machine for each task. However, the regressor is used at training along with the classifier, in order to add extra constraints on the network training and to enhance the loss function. This helps the network to learn a good representation of the scheduling problem and its parameters, also prevents the network from making some implicit mistakes in scheduling such as having two tasks executing on the same machine during the same range of time. \\

\subsubsection{Objective Function}
The cost function defined for this architecture is a sum of two criteria. The two criteria are categorical cross entropy \emph{(CE)} on the predicted machine to run a specific job $M_p$ and mean square error \emph{(MSE)} on the predicted actual start time $AST_p$ and the predicted actual finish time $AFT_p$. So, it can be summarized as follows:
\begin{equation}
\mathcal Loss(L) = CE(M_p, M_t) + MSE(AT_p, AT_t) \label{eq:l}
\end{equation}
where $M_p$ is the predicted machine, $M_t$ is the ground truth machine, $AT_p$ is the predicted actual time range and $AT_t$ is the ground truth actual time range. \\

\subsubsection{Drawbacks}
The main drawback of the proposed solution is that we have to know the maximum number of machines and the maximum number of tasks to be able to define the network. These numbers are used to define the network and loss function dimensions. So, the network design has to force some static scenarios to work on.
